%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{setspace}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,
    urlcolor=blue,
}
% \usepackage[left=0.25in, right=0.5in, top=1in, bottom=1in]{geometry}
% \nobibliography*
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
%\usepackage{palatino}
%\usepackage[default,light,bold]{sourceserifpro}
%\usepackage[urw-garamond]{mathdesign}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
%% \setlength{\resumewidth}{5.2in}
%% \setlength{\textwidth}{5.2in} % Text width of the document
\setlength{\parskip}{7pt}

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Mitchell T. Paulus} % Your name at the top

\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

\moveleft.5\hoffset\centerline{1408 Spring Ridge Ln} % Your address
\moveleft.5\hoffset\centerline{Flower Mound, TX 75028}
\moveleft.5\hoffset\centerline{(262) 483--9068, paulusm14@gmail.com}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

% \section{OBJECTIVE}

% Motivated college student with special interests in Mechanical Engineering and experience with food service, retail, and personal services. Proven track record of excellent performance and advancement.

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{EDUCATION}

\underline{{\textit{Ph.D. Mechanical Engineering,} Texas A\&M University, College Station}}\hfill 2012--2017

\parbox{11cm}{Dissertation title: ``Active Remote Setpoint Optimization Utilizing BAS Trend Data''}

\underline{{\sl M.S. Engineering,} Milwaukee School of Engineering} \hfill 2010--2012

\parbox{11cm}{Thesis title: ``Measurement, Modeling, Analysis and Reporting Protocols for Short-Term Monitoring and Verification of Whole Building Energy Performance''}

\underline{{\sl B.S. Mechanical Engineering,} Milwaukee School of Engineering} \hfill 2006--2010

\section{PROFESSIONAL CERTIFICATION}

ASHRAE Building Energy Modeling Professional (BEMP) \hfill 2020

Professional Engineer (Mechanical) \#135214, TX \hfill 2019

\vspace{0.1in}

\section{EXPERIENCE}

{\textit{Senior Energy Engineer} \hfill Sep 2017--Present} \\
Command Commissioning, LLC, Irving, TX

\begin{itemize}\itemsep -2pt % Reduce space between items
\item Lead development of data-driven analytics in existing building commissioning and Continuous Commissioning\textsuperscript{\textregistered{}}.
\item Deploy SpySpark installations and develop analytics and dashboards.
\item Develop enhanced sequences of operation along with measurement and verification of energy efficiency savings.
\item Develop whole building energy models for savings estimation and monitoring and verification of savings.
\item Conduct remote assessments and develop energy efficiency measures for Continuous Commissioning\textsuperscript{\copyright{}}.
\item Deployment of fault detection and diagnostics systems for existing building commissioning.
\end{itemize}

{\sl Postdoctoral Research Associate}  \hfill Sep 2017--Present \\
{\sl Graduate Assistant Researcher} \hfill Sep 2012--Sep 2017 \\
Energy Systems Laboratory, College Station, TX

\begin{itemize} \itemsep -2pt % Reduce space between items
    \item Lead software developer for Compass (cc-compass.tamu.edu), a building automation system (BAS) data analytics web application. Manage data for 800,000+ sensors and billions of data points.
    \item Manage and train Graduate Assistant Researchers and student workers.
    \item Develop algorithms for automated monitoring and verification of energy conservation projects and characterization of building component control sequences.
\end{itemize}

\vspace{10pt}

{\sl Research Assistant} \hfill Sep 2009--Feb 2012  \\
Milwaukee School of Engineering, Milwaukee, WI
\begin{itemize}\itemsep -2pt
\item Contracted through ASHRAE to complete research on the subject of short-term monitoring for long-term building energy prediction (RP-1404).
\item Completed model development and presented findings at semi-annual ASHRAE conferences.
\end{itemize}

\newcommand{\doi}[1]{\href{https://doi.org/#1}{#1}}

\section{PUBLICATIONS}
{\sl \textbf{Peer-Reviewed Journal Articles}}

\textbf{Mitchell T. Paulus}. Algorithm for explicit solution to the three parameter linear change point regression model.
\textit{Science and Technology for the Built Environment}, 2016. \href{https://doi.org/10.1080/23744731.2016.1267998}{10.1080/23744731.2016.1267998}.

Bass Abushakra and \textbf{Mitchell T. Paulus}.
An hourly hybrid multivariate change point inverse model using short-term monitored data for annual prediction of building energy performance, {Part III: Results and Analysis (1404-RP)}.
\textit{Science and Technology for the Built Environment}, 2016. \doi{10.1080/23744731.2016.1215659}.

Bass Abushakra and \textbf{Mitchell T. Paulus}.
An hourly hybrid multivariate change point inverse model using short-term monitored data for annual prediction of building energy performance, {Part II: Methodology (1404-RP)}.
\textit{Science and Technology for the Built Environment}, 2016. \doi{10.1080/23744731.2016.1215199}.

Bass Abushakra and \textbf{Mitchell T. Paulus}.
An hourly hybrid multivariate change point inverse model using short-term monitored data for annual prediction of building energy performance, {Part I: Background (1404-RP)}.
\textit{Science and Technology for the Built Environment}, 2016. \doi{10.1080/23744731.2016.1215222}.

\textbf{Mitchell T. Paulus}, David E. Claridge, and Charles Culp. Algorithm for automating the selection of a temperature dependent change point model.
\textit{Energy and buildings}, 2015. \href{https://doi.org/10.1016/j.enbuild.2014.11.033}{10.1016/j.enbuild.2014.11.033}.

Kavita Gangisetti, David E. Claridge, Jelena Srebric, and \textbf{Mitchell T. Paulus}. Influence of reduced {VAV} flow settings on indoor thermal comfort in an office space.
\textit{Building Simulation}, 2015. \href{https://doi.org/10.1007/s12273-015-0254-3}{10.1007/s12273-015-0254-3}.

{\sl \textbf{Book Chapters}}

Jan L.M. Hensen and Roberto Lamberts. \textit{Building Performance Simulation for Design and Operation, Expanded Second Edition}.
\href{https://doi.org/10.1201/9780429402296}{10.1201/9780429402296}.
David E. Claridge and \textbf{Mitchell T. Paulus}. Chapter 13: \textit{Building Simulation for Practical Operational Optimization}.


% David Strong and Victoria Burrows. \textit{A Whole-System Approach to High-Performance Green Buildings}. David E. Claridge, \textbf{Mitchell T. Paulus}, Charles Culp, and Kevin Christman, Chapter: \textit{Continuous Commissioning\textsuperscript{\textregistered{}}}, 2016

\textbf{\textit{Conference Presentations}}

``An Hourly Hybrid Multivariate Change Point Inverse  Model Using Short-Term Data for Annual Prediction of Building Energy and Performance: Results and Analysis'',\newline
2017 ASHRAE Winter Conference, Las Vegas, Seminar 62, Jan 2017

\textbf{\textit{Invited Presentations}}

``Neobem: The programmers choice for EnergyPlus'', ASHRAE Student Branch Meeting, Nov 4, 2021

``Reproducible Engineering'', Texas A\&M Mechanical Engineering Graduate
Student Organization (MEGSO) Technical Seminar, Apr 8, 2021

``Software Skills You Need to Know About: Part II'', ASHRAE Student Branch Meeting, Feb 12 2020

``CC\textsuperscript{\textregistered{}} for Mission Critical'', Texas Energy Summit, Austin, TX, Nov 12, 2019

``Software Skills/Tools You Should Know About as an Engineer'', ASHRAE Student Branch Meeting, Mar 21, 2018

``Software Designed for the Continuous Commissioning Process'', ASHRAE Student Branch Meeting, Sep 15, 2015

``Software to Assist in the CC Process'', Houston ASHRAE Chapter Student Night, Mar 2015

%----------------------------------------------------------------------------------------

\section{TEACHING EXPERIENCE}
\textbf{Graduate Teaching Fellow} \newline
Instructor of Record for MEEN 315, Principles of Thermodynamics \hfill Spring 2017

\textbf{Teaching Assistant}\newline
Energy Management in Commercial Buildings, MEEN 664, Texas A\&M \hfill \parbox[t]{1.5cm}{\raggedleft Fall 2016 \\ Fall 2015} \par

\vspace{10pt}

Application of Energy Management, MEEN 665, Texas A\&M \hfill \parbox[t]{2cm}{\raggedleft Spring 2017 \\ Spring 2016}

\vspace{10pt}
\textbf{Guest Lectures}
\begin{itemize}
    \item ``Time Constants and Measurements in Buildings'' \hfill Feb 21, 2017
    \item ``Ventilation and Economizers in Buildings'' \hfill Sep 20, 2016
    \item ``Buildings as RC Model and Thermal Zoning'' \hfill Sep 15, 2016
    \item ``Level 0 Continuous Commissioning Measures'' \hfill Mar 1, 2016
    \item  \parbox{10cm}{``Software Tools in the Continuous Commissioning Process''} \hfill Feb 4, 2016
    \item ``Calibrating Building Simulations'' \hfill Oct 2015
    \item ``Runge-Kutta Methods for Numerical Heat Transfer'' \hfill Jan 2012
\end{itemize}

\medskip


\textbf{Tutoring} \newline
Milwaukee School of Engineering \hfill 2011--2012

\section{LEADERSHIP EXPERIENCE}

President and Webmaster, Texas A\&M ASHRAE Student Branch \hfill 2015--2016

Member, Texas A\&M Mechanical Engineering Leadership Council \hfill 2014--2016

Head Coach, Texas A\&M Men's Club Volleyball \hfill 2014--2015\

President, MSOE ASHRAE Student Branch \hfill 2010--2011

\section{AWARDS}
Texas A\&M Graduate Teaching Fellow \hfill 2017

Fall MSOE Graduation Class Respondent \hfill 2010

ASHRAE Houston Scholarship \hfill 2014, 2015, 2016

WFIC Ladish Co. Scholarship \hfill 2009

Regal Scholarship \hfill 2006

\section{SOFTWARE}

Computer Programming: \parbox[t]{9cm}{C\#, JavaScript/TypeScript, Python, awk, shell, Matlab, SQL, Mathematica, VBA for Microsoft Office}

Building Simulation: \parbox[t]{10cm}{EnergyPlus/OpenStudio, eQuest, Carrier's
HAP, WinAM, Inverse Modeling Toolkit}

Web Development: \parbox[t]{10cm}{Model-View-Controller Architecture,
html/css/javascript, jQuery, knockout.js, d3.js}

Database Management: SQL Server Management Studio

Solid Modeling: ANSYS, Pro Engineer, SolidWorks/SolidEdge

Other: SkySpark/axon, Git, bazaar, make, redo, ANTLR, \LaTeX, GIMP, Vim

\section{PROFESSIONAL SOCIETIES}

\parbox[t]{9cm}{American Society of Heating, Refrigerating, and Air-Conditioning Engineers (ASHRAE)} \hfill \parbox[t]{3cm}{\raggedleft  Assoc. Member \\ 2011--Pres.}

\parbox[t]{9cm}{ASHRAE Technical Committee 4.7, Energy Calculations }\hfill \parbox[t]{3cm}{\raggedleft Corres. Member \\ 2015--Pres.}

\section{OUTREACH}
\parbox[t]{10cm}{Contributed to 2017 ASHRAE Fundamentals Handbook, \textit{Energy Estimating and Modeling Methods} Chapter}

Texas A\&M Freshman Student Informational \hfill Dec 2015\\
\strut \hfill Mar 2016

Texas A\&M Mechanical Engineering Leadership Council \hfill 2015--2017

\section{RESEARCH INTERESTS}

Energy efficiency and conservation, particularly focused on buildings

Software and web application development

Continuous Commissioning\textsuperscript{\textregistered{}}

Data-driven building energy modeling

\section{REVIEWING}

\href{https://www.sciencedirect.com/journal/energy}{Energy}

\href{https://www.sciencedirect.com/journal/energy-and-buildings}{Energy and Buildings}

%% Science and Technology for the Built Environment

\href{https://www.tandfonline.com/journals/tbps20}{Journal of Building Performance Simulation}

\href{https://www.springer.com/journal/12273}{Building Simulation}

ASHRAE Conference Papers

\end{resume}
% \bibliographystyle{plain}
% \nobibliography{Thesis}
\end{document}
